Your Title Goes Here

### 2018-01-04 documentation/documentation.tex
adding tweepy, sorting doo, ading chi student id

\begin{titlepage}
	\begin{figure}
	\centering
	\includegraphics[scale=0.32]{logohsg}
	\end{figure}
\centering
\centering
{\scshape\large School of Management, Economics, Law, Social Sciences and International Affairs \par}
\vspace{1.7cm}
{\huge\bfseries The effect of Twitter activity on \\ Bitcoin price\par}
\vspace{1.0cm}
{\Huge\itshape Documentation\par}
\vspace{1.0cm}     
{\Large Software Engineering for Economists \\ (7,610,1.00) \par}
\vspace{1.2cm}
{Alen Stepic - 11-475-258 \\ Dimitrios Koumnakes - 10-613-370 \\ Severin Kranz - 13-606-355 \\ Joël Sonderegger - 11-495-488 \\ Chi Xu - XX-XXX-XXX \par}
\vspace{1.2cm}
Fall Term 2017 \\
\vspace{1.2cm}
{Supervisor\\ Prof. Dr. Philipp Zahn\\ FGN HSG\\ Varnbüelstrasse 19\\ 9000 St. Gallen\\ Department of Economics\par}
\vspace{0.8cm}
{\centering\today\par}
\end{titlepage}

@@

\section{Data Collection}
This section contains a detailed description of how the data for the sequential analysis is gathered and stored. Two separate data sets will be collected: (1) Tweets data and  (2) Bitcoin price index data.
\subsection{Tweets Data}
Whit the Python script real-time Twitter data are streamed and stored. This happens with help of a Raspberry Pi.
\subsubsection{Python Script}
Twitter offers different API for collecting data. However, the time frame for gathering data on a freely base with full access is limited to 7 days \parencite{twitterinc2017a}. On the other hand, Python offers different twitter libraries. Such as the open-source package tweepy. This package has been used for streaming the twitter data as it simplify the script and enables to gather a broader number of tweets for free.

Tweepy is
TBD
TBD
TBD

@@

To obtain the mentioned keys and tokens a twitter account is needed. Once, a twitter account exist a application has to be created. This has to be conducted by login with the twitter account credentials under the following link: 
\begin{lstlisting}[language=bash]
%https://apps.twitter.com/
\end{lstlisting}

@@

\begin{flushleft}
................................\\
Alen Stepic - 11-475-258\\\bigskip\bigskip  
................................\\
Dimitrios Koumnakes - 10-613-370\\\bigskip\bigskip
................................\\
Severin Kranz - 13-606-355\\\bigskip\bigskip
................................\\
Joël Sonderegger - 11-495-488\\\bigskip\bigskip
................................\\
Chi Xu - XX-XXX-XXX

>>>>

\begin{titlepage}
	\begin{figure}
	\centering
	\includegraphics[scale=0.32]{logohsg}
	\end{figure}
\centering
\centering
{\scshape\large School of Management, Economics, Law, Social Sciences and International Affairs \par}
\vspace{1.7cm}
{\huge\bfseries The effect of Twitter activity on \\ Bitcoin price\par}
\vspace{1.0cm}
{\Huge\itshape Documentation\par}
\vspace{1.0cm}     
{\Large Software Engineering for Economists \\ (7,610,1.00) \par}
\vspace{1.2cm}
{Alen Stepic - 11-475-258 \\ Dimitrios Koumnakes - 10-613-370 \\ Severin Kranz - 13-606-355 \\ Joël Sonderegger - 11-495-488 \\ Chi Xu - 16-300-915 \par}
\vspace{1.2cm}
Fall Term 2017 \\
\vspace{1.2cm}
{Supervisor\\ Prof. Dr. Philipp Zahn\\ FGN HSG\\ Varnbüelstrasse 19\\ 9000 St. Gallen\\ Department of Economics\par}
\vspace{0.8cm}
{\centering\today\par}
\end{titlepage}

@@

\section{Data Collection}
This section contains a detailed description of how the data for the sequential analysis is gathered and stored. Two separate data sets will be collected: (1) Tweets data and  (2) Bitcoin price index data.
\subsection{Tweets Data}
Whit the Python script real-time Twitter data are streamed and stored. This happens with help of a Raspberry Pi.
\subsubsection{Python Script}
Twitter offers different API for collecting data. However, the time frame for gathering data on a freely base with full access is limited to 7 days \parencite{twitterinc2017a}. On the other hand, Python offers different twitter libraries. Such as the open-source package tweepy.

\paragraph{Tweepy}\mbox{}\\{}
Tweepy is a open-source libary. It provides a simple way to gather real time tweets, by managing authentication, connection and tweet information of Twitters streaming API. The tweepy instance tweepy.streaming is used for the streaming session and forwards the data to the StreamListener instance. The \verb|class listener(StreamListener)| calls the method \verb|def on_data(self, data)|. With this method all data of filtered tweets are gathered in real time. The main function \verb|def main()| manages the required authentication as follow:
\begin{lstlisting}[language=bash]
auth = OAuthHandler (ckey, csecret)
auth.set_access_token(atoken, asecret)
\end{lstlisting}
Those authentications are demanded by twitter and explained in more details in the next paragraph. Furthermore, the main function starts the running of the stream, while filtering for the buzzword bitcoin by processing \verb|twitterStream.filter(track=["bitcoin"]|. Tweepy has been applied for this assignment because it simplify the script and enables to gather a huge number of tweets for free.

@@

To obtain the mentioned keys and tokens a twitter account is needed. Once, a twitter account exist a application has to be created. This has to be conducted by login with the twitter account credentials under the following link: 
\begin{lstlisting}[language=bash]
https://apps.twitter.com/
\end{lstlisting}

@@

\begin{flushleft}
Alen Stepic - 11-475-258\\\bigskip\bigskip  
Dimitrios Koumnakes - 10-613-370\\\bigskip\bigskip
Severin Kranz - 13-606-355\\\bigskip\bigskip
Joël Sonderegger - 11-495-488\\\bigskip\bigskip
Chi Xu - 16-300-915
